\plaintitle

### 2018-04-05 paper/paper.tex
...

When a user wants to compare the latest \tt{README.md} file
with the same file from 2 versions before,
he might try to use \tt{git} with an argument
``\verb|HEAD^^|''
for specifying an old version.

@@

Nothing happens here because
\verb|HEAD^^|
specifies a file included in the older commit,
and the command above only compares the \tt{README.md}
with the file included in an old commit, where
\tt{README.md} might be the same as the latest version.

If {\GH} is installed,
the user can type a special shortcut key
% (e.g. \tt{Cmd-Ctrl-G})
to invoke {\GH} after typing ``\verb|git RE 2|'' to see how he can do the job.

\begin{figure}[h]
  \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
  \caption{Invoking {\GH}.}
  \label{bash1}
\end{figure}

Here, various candidate entries with
descriptios and command strings are listed.
One of the entries says ``Compare README.md with the one from 2 versions before''.
% which means ``to compare \tt{README.md} with the one from 2 versions before.''
%
If the user thinks that that's what he wants to do,
he can select the entry by selecting it by typing arrow keys
and type the enter key.
Then the user's input string is replaced by the right command string
that satisfies the user's need.

A description like ``2 days ago'' is also shown in the candidate list.
This means that the user can use the same string ``\tt{git RE 2}''
for getting the \tt{README.md} file of the day before yesterday.
The command,
``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff '@{2 days ago}' README.md|}'',
is difficult to remember,
but users can do the same thing only by saying \sqtt{RE} and \sqtt{2}.

A Japanese \stt{git} user can do the same thing just like
English-speaking users.

@@

If the user wants to know more about the command line options,
he can click the
\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{figures/info-xxl.png}}
button and browse the Wiki page.
The page can be edited by any user, and

>>>>

When a user wants to compare the latest \tt{README.md} file
with the same file from 2 versions before,
he might try to use \tt{git} with an argument
``\verb|HEAD^^|''
for specifying the old version.

@@

However, nothing happens here because
\verb|HEAD^^|
specifies a file included in the older commit,
and the command above only compares the \stt{README.md}
with the file included in an old commit, where
\stt{README.md} might be the same as the latest version.

If {\GH} is installed,
the user can type a special shortcut key
% (e.g. \tt{Cmd-Ctrl-G})
to invoke {\GH} after typing \stt{git RE 2} to see how he can
perform the task.

\begin{figure}[h]
  \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
  \caption{Invoking {\GH} after typing \stt{git rea 2}.}
  \label{bash1}
\end{figure}

Here, various candidate entries with
descriptios and command strings are listed.
One of the entries says
``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}''.
If the user thinks that that's what he wants to do,
he can select the entry by typing arrow keys and type the enter key.
Then the user's input string is replaced by the right command string
that satisfies the user's need.

A description like ``2 days ago'' is also shown in the candidate list.
This means that the user can use the same string \sqtt{git RE 2}
for getting the \stt{README.md} file of the day before yesterday.
The command,
``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff '@{2 days ago}' README.md|}'',
may not be familiar to most \tt{git} users,
but users can perform this task only by giving \sqtt{RE} and \sqtt{2}.

A Japanese \stt{git} user can do the same thing just like
English-speaking users.
He can user the term \qtt{比}(compare) to find how he can perfor the job.

@@

If the user wants to know more about the command line,
he can click the
\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{figures/info-xxl.png}}
button and see the Wiki page shown in Figure \ref{scrapboxpage}.
The user can edit the page if he wants to add information or finds an error.
